### 2018-05-07 Paper/method.tex
..

\begin{center}
\begin{tikzpicture}[node distance=1.5cm]

@@

\node (dr) [draw, diamond, aspect=2.0] {Is \\ Dimension-reduction \\ possible$?$};

@@

>>>>

\begin{figure}[htbp]
\begin{center}
\begin{tikzpicture}[node distance=1.5cm]

@@

\node (dr) [draw, diamond, aspect=1.5,yshift=-6.7cm, text width=4.5em, text centered] {Is DR possible$?$};

\draw [line] (screen) -- (dr);

%\node (dr_mean) [right of=dr, xshift=5cm] {DR: Dimension Reduction};

@@

\caption{Flow-diagram outlining the overall strategy for constructing reduced-order surrogates using
the derivative-based sensitivity measures. Note that DR is an abbreviation for dimension reduction.}
\end{figure}
